Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-21 journal/article.tex
Success: Commitment and urgency

>>>>

\subsubsection{Urgency and commitment to change}

% Make it understood that there is no return to the old model

To make a large organization change the direction of the change needs to be
communicated clearly. Atriculating urgency at start will help getting the change
under way [P49]. Feedback of changes should certainly be listened to, but in the
end it must be made clear that the old model can not be returned to [P22].
For a case where the organization was changed all at once it was reported that
the magnitude of change helped created the impression that the change was non
negotiable [P11]. Firstly, as it vas evident that a large change was to happen
people felt encouragement and permission to move on from the old way, and
secondly, the urgency eliminated wasteful discussions on wheter Scrum was a good
model or not [P11].
When the organization culture is ingrown he change vision must constantly be
reminded of, and each step towards the new model consider a victory [P48].
